Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-02-25 phaseDelay.tex
Updates from ShareLaTeX

Also, concerns with the phase delay  had
 a significant impact on the history of agile programming. Kent Beck is
 particulary eloquent

@@

>>>>

\begin{center}
\includegraphics[width=3.3in]{beckB4.png}

\includegraphics[width=3.3in]{beckAFTER.png}
\end{center}

Also, concerns with the phase delay  had
 a significant impact on the history of agile programming. Kent Beck is
 particularly eloquent

@@

The software development community has spent enormous resources in recent decades trying to reduce the cost of change—better languages, better database technology, better programming practices, better environments and tools, new notations.

What would we do if all that investment paid off? What if all that work on languages and databases and whatnot actually got somewhere? What if the cost of change didn't rise exponentially over

This is one of the premises of XP. It is the technical premise of XP. If the cost of change rose slowly over time, you would act completely differently from how you do under the assumption that costs rise exponentially. You would make big decisions as late in the process as possible, to defer the cost of making the decisions and to have the greatest possible chance that they would be right. You would only implement what you had to, in hopes that the needs you anticipate for tomorrow wouldn't come true. You would introduce elements to the design only as they simplified existing code or made writing the next bit of code simpler.
￼
time, but rose much more slowly, eventually reaching an asymptote? What if tomorrow's software engineering professor draws Figure 3 on the board?
